```{r setup, include = F}
options(java.parameters = "-Xmx16G")
library(tidyverse)
library(lubridate)
library(haven)
library(RJDBC)
library(knitr)
library(rmarkdown)
setwd("N:/")

# Just for sample runs
d = 10
assessment_summary = read_csv("C:/Users/CA19130/Downloads/assessment_summary.csv")
tvaas_summary = read_csv("C:/Users/CA19130/Downloads/tvaas_summary.csv")
# absenteeism_summary = read_csv("C:/Users/CA19130/Downloads/absenteeism_summary.csv")
```
---
title: "District Summary Report"
author: "Tennessee Department of Education"
date: `r str_c(month(today(), label = T, abbr = F), " ", day(today()), ", ", year(today()))`
output: html_document `r #change to pdf_document?`
params:
    d: `r d`
---

```{r data, include = F}
# Data 
assessment = filter(assessment_summary, system == d)
tvaas = filter(tvaas_summary, system == d)
# absenteeism = filter(absenteeism_summary, system == d)
```

### Document Overview
This document provides an overview of assessment, TVAAS, and absenteeism data for `r unique(assessment$system_name)`. Please direct any questions or concerns to [our Accountability team](mailto:TNED.Accountability@tn.gov).

### Assessment Results
Below is a high-level summary of `r unique(assessment$system_name)`'s assessment results.

```{r assessment, include = F}
# How did your proficiency compare to last year? 
improve = case_when(
  unique(assessment$pct_on_mastered_district[assessment$year == max(assessment$year)]) - unique(assessment$pct_on_mastered_district[assessment$year == min(assessment$year)]) > 0.5 ~ "improved",
  unique(assessment$pct_on_mastered_district[assessment$year == max(assessment$year)]) - unique(assessment$pct_on_mastered_district[assessment$year == min(assessment$year)]) < -0.5 ~ "declined",
  T ~ "stayed about the same"
)
# Comparison to CORE region and the state? 
region = case_when(
  unique(assessment$pct_on_mastered_district[assessment$year == max(assessment$year)]) > 0.5 + unique(assessment$pct_on_mastered_region[assessment$year == max(assessment$year)]) ~ "better than",
  unique(assessment$pct_on_mastered_district[assessment$year == max(assessment$year)]) < unique(assessment$pct_on_mastered_region[assessment$year == max(assessment$year)]) - 0.5 ~ "worse than",
  T ~ "about the same as"
)
state = case_when(
  unique(assessment$pct_on_mastered_district[assessment$year == max(assessment$year)]) > 0.5 + unique(assessment$pct_on_mastered_state[assessment$year == max(assessment$year)]) ~ "better than",
  unique(assessment$pct_on_mastered_district[assessment$year == max(assessment$year)]) < unique(assessment$pct_on_mastered_state[assessment$year == max(assessment$year)]) - 0.5 ~ "worse than",
  T ~ "about the same as"
)
# Which of your schools has the highest proficiency?
best = filter(assessment, year == max(year)) %>% 
  filter(pct_on_mastered == max(pct_on_mastered))
# Lowest?
worst = filter(assessment, year == max(year)) %>% 
  filter(pct_on_mastered == min(pct_on_mastered))
# Which of your schools are improving most? 
fastest_improving = select(assessment, year:pct_on_mastered) %>% 
  spread(year, pct_on_mastered) 
names(fastest_improving) = c("region", "system", "system_name", "school", "school_name", "lag2", "lag1", "current")
fastest_improving = mutate(fastest_improving, diff = current - lag2) %>% 
  filter(diff == max(diff, na.rm = T))
# Least?
slowest_improving = select(assessment, year:pct_on_mastered) %>% 
  spread(year, pct_on_mastered) 
names(slowest_improving) = c("region", "system", "system_name", "school", "school_name", "lag2", "lag1", "current")
slowest_improving = mutate(slowest_improving, diff = current - lag2) %>% 
  filter(diff == min(diff, na.rm = T))
```

- Proficiency rates in `r unique(assessment$system_name)` have __`r improve`__ over the past two years (`r unique(assessment$pct_on_mastered_district[assessment$year == min(assessment$year)])`% to `r unique(assessment$pct_on_mastered_district[assessment$year == max(assessment$year)])`%).
- `r unique(assessment$system_name)` is performing __`r region`__ the rest of the `r unique(assessment$region)` region and __`r state`__ the state.
- `r unique(best$school_name)` had the __highest proficiency__ of all schools in the district last year (`r unique(best$pct_on_mastered)`%). 
- `r unique(worst$school_name)` had the __lowest proficiency__ of all schools in the district last year (`r unique(worst$pct_on_mastered)`%).
- `r unique(fastest_improving$school_name)`'s proficiency __has `r ifelse(unique(fastest_improving$diff) > 0, "improved most", "declined least")`__ over the past two years.
- `r unique(slowest_improving$school_name)`'s proficiency __has `r ifelse(unique(slowest_improving$diff) > 0, "improved least", "declined most")`__ over the past two years.

### TVAAS 
Below is a high-level summary of `r unique(assessment$system_name)`'s TVAAS performance. You can learn more about TVAAS [here](https://www.tn.gov/education/data/tvaas.html), and you can view your district's results in more detail on the [TVAAS secure site](https://tvaas.sas.com/).

```{r tvaas, include = F}
# District composite
# What proportion of schools are a TVAAS level 4/5? 
# What proportion have been a level 4/5 for the past two years? 
# How does that compare to the region and the state?
region = case_when(
  unique(tvaas$pct_high_tvaas_district) > 0.5 + unique(tvaas$pct_high_tvaas_region) ~ "higher than",
  unique(tvaas$pct_high_tvaas_district) < unique(tvaas$pct_high_tvaas_region) - 0.5 ~ "lower than", 
  T ~ "about the same as"
)
state = case_when(
  unique(tvaas$pct_high_tvaas_district) > 0.5 + unique(tvaas$pct_high_tvaas_state) ~ "higher than",
  unique(tvaas$pct_high_tvaas_district) < unique(tvaas$pct_high_tvaas_state) - 0.5 ~ "lower than", 
  T ~ "about the same as"
)
region_2yr = case_when(
  unique(tvaas$pct_high_tvaas_2yr_district) > 0.5 + unique(tvaas$pct_high_tvaas_2yr_region) ~ "higher than",
  unique(tvaas$pct_high_tvaas_2yr_district) < unique(tvaas$pct_high_tvaas_2yr_region) - 0.5 ~ "lower than", 
  T ~ "about the same as"
)
state_2yr = case_when(
  unique(tvaas$pct_high_tvaas_2yr_district) > 0.5 + unique(tvaas$pct_high_tvaas_2yr_state) ~ "higher than",
  unique(tvaas$pct_high_tvaas_2yr_district) < unique(tvaas$pct_high_tvaas_2yr_state) - 0.5 ~ "lower than", 
  T ~ "about the same as"
)
```
- Last year `r unique(tvaas$system_name)` earned a __TVAAS level `r unique(tvaas$district_tvaas)`__, compared to a level `r unique(tvaas$district_tvaas_lag)` the year before. 
- `r unique(tvaas$pct_high_tvaas_district)`% of schools in `r unique(tvaas$system_name)` earned a TVAAS level 4 or 5 last year, which was __`r region`__ the rest of the `r unique(tvaas$region)` region and __`r state`__ the rest of the state.
- `r unique(tvaas$pct_high_tvaas_2yr_district)`% of schools in your district earned a TVAAS level 4 or 5 in **both** of the last two years, which was __`r region_2yr`__ the rest of the region and __`r state_2yr`__ the state.

### Absenteeism

```{r absenteeism, include = F}

```

### Achievement Gaps

```{r achievement_gaps, include = F}

```

### Plots

``` {r plots, echo = F, warning = F}

```

